\documentclass{article}
\usepackage{float}
\usepackage[pdftex]{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[cm]{fullpage}
\lstset{basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}
\begin{document}

\author{Jon Robison}
\title{CS595 Assignment 10}
\maketitle

Q1.\\
Choose a blog or a newsfeed (or something similar with an Atom or RSS feed).  It should be on a topic or\\
topics of which you are qualified to provide classification training data. Find something with at least \\
100 entries Create between four and eight different categories for the entries in the feed:..download and process.\\*

The program getTitles.py retrieves the paginated results and outputs to a pipe separated text\\
file. This file is then manually processed to include necessary training information. This is \\
accomplished by putting the feature in the 3rd location and the actual category in the 4th \\
location (after the third pipe) when appropriate.\\*

See program given in Appendix A.\\*

Q2.\\
Manually classify the first 50 entries, and then classify (using the fisher classifier) the remaining\\
50 entries. Create a table with the title, the string used for classification, cprob(), predicted category,\\
and actual category.\\*

The driver program invokes docclass, reading the file given from A. This trains the classifier with the\\
first half of whatever is given in the file, and guesses the last half. Different results are printed to a\\
latex file and the console for the results table and debugging information/status, respectively.\\*

\input{q2/classificationResults.tex}
\\*

CProb is notably low, indicating low confidence in the guess. My believe is that since the blog is a music\\
blog, and the titles are typically band or album names, the classifier can't distinguish titles. I initially\\
went with this blog since it already broke down the classifications for me, but realized upon identifying the\\
features it wouldn't be great since the classications were the only unique data. That would be my next step.\\*

See program given in Appendix B and C.\\*

Q3.\\
Assess the performance of your classifier in each of your categories by computing precision and recall.  Note\\
that the definitions are slightly different in the context of classification.\\*

\begin{tabular}{ l l l }
	&Precision	&Recall\\
album	&19/34		&19/19\\
new	&1/1		&1/5\\
event	&10/10		&10/22\\
single	&3/3		&3/4\\
interview&0/2		&0/0\\
\end{tabular}

\appendix
\newpage
Appendix A
\lstinputlisting[language=python]{q1/getTitles.py}

\newpage
Appendix B
\lstinputlisting[language=python]{q2/driver.py}

Appendix C
\lstinputlisting[language=python]{q2/docclass.py}
\end{document}
