\documentclass{article}
\usepackage[pdftex]{graphicx}
\usepackage{verbatim}
\usepackage{listings}
\begin{document}

\author{Jon Robison}
\title{CS595 Assignment 3}
\maketitle

Q1. Download the 1000 URIs from assignment 2...remove formatting \\
Large collection of files included in modified/ directory
See Appendix A for download program
\\*

Q2. Choose a query term...to ten documents...compute TFIDF values for the term
in each of the 10 documents. \\
\verbatiminput{q2/results}%
See Appendix B for scripts to produce table
\\*

Q3. Now rank the same 10 URIs from question 2, but this time by their
PageRank. \\
\verbatiminput{q3/results}%
Briefly compare and contrast the rankings produced in questions 2
and 3.

A3: Top TFIDF was floydmayweather.com. This was one of two non-zero scoring
options, and I infer TFIDF was heavily weighted in the pagerank calculation.
This would result in being calculated as number one. themoneyteam.com on the
other hand is relatively low TFIDF, but is a domain in and of itself, thus
disproportionately large TFIDF. It is unfortunate the other pages weren't
page ranked, but I predict they would have linearly small results.

\newpage
\appendix
Appendix A
\lstinputlisting[language=bash,caption={Downloads via curl and lynxifies product to produce a more easily searchable/indexable file}]{q1/download}

\newpage
Appendix B
\lstinputlisting[language=bash,caption={Control runscript to launch other utils}]{q2/run}
\lstinputlisting[language=bash,caption={Script taking arguments to calculate single TFIDF}]{q2/tfidf}
\lstinputlisting[language=bash,caption={Copied first ten files matching criteria passed in}]{q2/copyTen}

\end{document} 
