\documentclass{article}
\usepackage{float}
\usepackage[pdftex]{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\lstset{basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}
\begin{document}

\author{Jon Robison}
\title{CS595 Assignment 8}
\maketitle

Q1. \\
See Appendix A for changes to recommendations.py\\
See Appendix B for driver.py\\*

1.  What 5 movies have the highest average ratings? Show the movies\\
and their ratings sorted by their average ratings.\\*
\begin{tabular}{ l r }
Marlene Dietrich: Shadow and Light (1996) & 5.0 \\
Aiqing wansui (1994) & 5.0 \\
Prefontaine (1997) & 5.0 \\
Great Day in Harlem, A (1994) & 5.0 \\
Santa with Muscles (1996) & 5.0 \\
\end{tabular}
\\*

2.  What 5 movies received the most ratings? Show the movies and\\
the number of ratings sorted by number of ratings.\\*
\begin{tabular}{ l r }
Liar Liar (1997)& 485 \\
Return of the Jedi (1983) & 507 \\
Fargo (1996) & 508 \\
Contact (1997) & 509 \\
Star Wars (1977) & 583 \\
\end{tabular}
\\*

3.  What 5 movies were rated the highest on average by women? Show\\
the movies and their ratings sorted by ratings.\\*
\begin{tabular}{ l r }
Mina Tannenbaum (1994) & 5.0 \\
Year of the Horse (1997) & 5.0 \\
Foreign Correspondent (1940) & 5.0 \\
Telling Lies in America (1997) & 5.0 \\
Prefontaine (1997) & 5.0 \\
\end{tabular}
\\*

4.  What 5 movies were rated the highest on average by men? Show\\
the movies and their ratings sorted by ratings.\\*
\begin{tabular}{ l r }
Love Serenade (1996) & 5.0 \\
Leading Man, The (1996) & 5.0 \\
Great Day in Harlem, A (1994) & 5.0 \\
Delta of Venus (1994) & 5.0 \\
Santa with Muscles (1996) & 5.0 \\
\end{tabular}
\\*

5.  What movie received ratings most like Top Gun? Which movie\\
received ratings that were least like Top Gun (negative correlation)?\\*
Babyfever (1994), 1.0\\
Wooden Man's Bride, The (Wu Kui) (1994), 0
\\*

6.  Which 5 raters rated the most films? Show the raters' IDs and\\
the number of films each rated.\\*
\begin{tabular}{ l r }
276 & 516 \\
450 & 538 \\
13 & 632 \\
655 & 678 \\
405 & 736 \\
\end{tabular}
\\*

7.  Which 5 raters most agreed with each other? Show the raters'\\
IDs and Pearson's r, sorted by r.\\*
\begin{tabular}{ l c r }
341 & 143 & 1.0 \\
810 & 135 & 1.0 \\
813 & 756 & 1.0 \\
349 & 46 & 1.0 \\
889 & 772 & 1.0 \\
\end{tabular}
\\*

8.  Which 5 raters most disagreed with each other (negative\\
correlation)? Show the raters' IDs and Pearson's r, sorted by r.\\*
\begin{tabular}{ l c r }
60 & 872 & -1.0 \\
793 & 412 & -1.0 \\
344 & 598 & -1.0 \\
340 & 203 & -1.0 \\
340 & 68 & -1.0 \\
\end{tabular}
\\*

9.  What movie was rated highest on average by men over 40? By men\\
under 40?\\*
\begin{tabular}{ l r }
Prefontaine (1997) & 5.0 \\
Grateful Dead (1995) & 5.0 \\
Marlene Dietrich: Shadow and Light (1996) & 5.0 \\
Faithful (1996) & 5.0 \\
Hearts and Minds (1996) & 5.0 \\
\end{tabular}
\\*

10. What movie was rated highest on average by women over 40? By\\
women under 40?\\*
\begin{tabular}{ l r }
Love Serenade (1996) & 5.0 \\
Leading Man, The (1996) & 5.0 \\
Crossfire (1947) & 5.0 \\
Santa with Muscles (1996) & 5.0 \\
Delta of Venus (1994) & 5.0 \\
\end{tabular}
\\*

\appendix
\newpage
Appendix A
\lstinputlisting[language=python]{recommendations.py}

\newpage
Appendix B
\lstinputlisting[language=python]{driver.py}

\end{document}
